Using Fundamental Measure Theory to treat the Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2013-08-22 papers/pair-correlation/paper.tex
modified math in paper and merged some pulled python stuff Tested everything on node22.

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-alt-3.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.3, plotted when
    $\rr_1$ and $\rr_2$ are in contact.  The color plot on the left
    shows the triplet distribution function, with white corresponding
    to the contact value of the \emph{pair} distribution function.
    The plot on the right shows the value of $g^{(3)}$ along the path
    shown as a dotted lin on the plot to the
    left.}\label{fig:triplet-distribution-3}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-alt-4.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.3, plotted when
    $\rr_1$ and $\rr_2$ are in contact.  The color plot on the left
    shows the triplet distribution function, with white corresponding
    to the contact value of the \emph{pair} distribution function.
    The plot on the right shows the value of $g^{(3)}$ along the path
    shown as a dotted lin on the plot to the
    left.}\label{fig:triplet-distribution-4}
\end{figure}

@@

  \tfrac1{\sigma}\right) + \cdots \right)

@@

  4\pi\sigma^2 n g_\sigma \delta +
  4\pi\sigma^2 n \left(\tfrac{g_\sigma'}{2} + \tfrac{2}{\sigma}\right)

@@

  - \tfrac{1}{2}\left(4\pi\sigma^2ng_\sigma\right)^2\delta^2 + \mathcal{O}(\delta^3)

@@

@@

      \sigma^2}}{4\pi\sigma^2nkT}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-alt-3.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ plotted when $\rr_1$ and $\rr_2$ are
    in contact.}\label{fig:triplet-distribution-3}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-alt-4.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:triplet-distribution-4}
\end{figure}

@@

  \frac{g_\sigma}{\sigma}\right)\delta^2 + \cdots \right)

@@

  2\pi\sigma^2 n N g_\sigma \delta +
  \pi\sigma n N  \left(g_\sigma'\sigma + 2g\right)

@@

  - 2\pi^2\sigma^4n^2N^2\sigma^4g_\sigma^2\delta^2 + \mathcal{O}(\delta^3)

@@

So that
  \frac{\partial Z}{\partial \sigma} =
  -2ZnN\pi\sigma^2g_\sigma\\
  \frac{\partial^2 Z}{\partial \sigma^2} =
  -2ZnN\pi\sigma\left(g_\sigma'\sigma + 2g\sigma \right)
  +4Zn^2N^2\sigma^4g^2

@@

      \sigma^2}}{2\pi\sigma^2nkT}
